\sysfull

### 2018-04-14 paper/background.tex
last part of background revised - commented out the last paragraph added by Amjad: repeats what earlier paragraph said

Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is a programming challenge, given fixed hardware with a fixed energy buffering capacity. Buffer sizes from prior work vary widely from 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo}. Sizing tasks complicates {\em porting} code from one device to another. An excessively costly task on a device with a small energy buffer may be a relatively short, task on a device with a larger buffer. The key problem is that using existing systems, by defining tasks statically for a fixed energy buffer, the programmer either risks non-termination or poor performance due to high overhead. \sys's {\em task coalescing}, described in Section~\ref{sec:task_coalescing}, is motivated by these observations.

\textbf{Motivating the Design of \sys's Execution Model.} The challenge of \emph{efficiently} executing a program under frequent power failures, lies in the fact that the program needs to be energy aware. This challenge becomes even bigger when \emph{generality} is a design requirement and such the system must not require a specific hardware circuitry to offer its efficiency. \emph{Flexibility} is a key for wide adaptation, therefore, \sys's execution model should not limit the programmer to a subset of the functionality of the underlying software technology. \emph{\sys champions an efficient, general, and flexible intermittent execution.}

>>>>

Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is a programming challenge, given fixed hardware (no support from dedicated circuitry to measure the state of energy buffer) with a fixed energy buffering capacity. Buffer sizes from prior work on intermittently-powered computing hardware vary widely from 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo}. Sizing tasks complicates {\em porting} code from one device to another. An excessively costly task on a device with a small energy buffer may be a relatively short task on a device with a larger buffer. The key problem is that using existing systems, by defining tasks statically for a fixed energy buffer, the programmer either risks non-termination or poor performance due to high overhead. \sys's execution model based on {\em task coalescing}---merging or dissecting multiple tasks {\em during} execution based on the program execution behavior, and {\em task downscaling}---shortening task boundaries during execution when even the smallest task does not fit the energy buffer, both models described in Section~\ref{sec:task_adaptation}, is motivated by these observations.

%\textbf{Motivating the Design of \sys's Execution Model.} The challenge of \em{efficiently} executing a program under frequent power failures, lies in the fact the the program needs to be energy aware. This challenge becomes even bigger when \em{generality} is a design requirement and such the system must not require a specific hardware circuitry to offer its efficiency. \em{Fllexibility} is key for wide adaptation, therefore, \sys's execution model should not limit the programmer to a subset of the functionality of the underlying software technology. \em{\sys champions an efficient, general, and flexible intermittent execution.}
